Group 5 Report

### 2022-08-01 Report/Group 5 report.Rmd
La til limitations and steps forward-delen

@@

>>>>

## Problem statement

@@

During the case we realized that we had to limit our solution. The case 
presented by OPX wanted an automated code which would retrieve the data 
and calculate the different KPIs, which turned out not to be possible. 
The limitations can be divided into problems regarding: 
(i) the accessible data, and 
(ii) the non-accessible data

The limitation with the accessible data is first and foremost the lack of 
relevant data in the annual reports from the NGOs.  Since there is no 
obligation to provide annual accounts, they often have more information 
about the organization in general rather than numbers. If they do provide 
the annual accounts, they are not standardized. This means that different 
NGOs do not have an established template for what the different posts in 
the annual accounts should contain.

Also, these annual reports themselves appear in different formats. If they 
do appear in the same format, the accounts we want to retrieve are often 
in an image format rather than text. The lack of data, standardization and 
diverse formats made it impossible to create an automated solution for 
collecting data based on the NGOs’ annual reports.

The limitation with the non-accessible data is that the data OPX needs to 
calculate the different KPIs do not exist in the annual reports.  We 
experimented with an annual report from Brønnøysundregisteret. Although 
the reports were standardized, the different posts in the report did not 
match the template from OPX. Additionally the data that OPX is interested 
in and which is necessary for calculating the relevant KPIs are not 
available.

Also, with limited experience with KPIs it was hard to sort out which ones 
that would be of relevance and not. After examining the different 
alternatives, we concluded that the NGOs could report in a standardized 
excel document from which our code retrieves the data to calculate the KPIs.

In addition, we looked at the draft of a new law on associations from 2021 
by the Ministry of Trade, Industries, and Fisheries, to see if it contained 
changes in the laws regarding annual reports, which would have made the data 
needed available in the future. This turned out to be a dead end, as the 
draft focused largely on smaller and local associations and contained no 
changes in reporting obligations. Therefore, if this law were to be 
implemented, it would not be of any relevance to OPX. As a result, due to 
OPX’s need for this data to be available, we recommend discussions with 
relevant politicians and ministry officials as a starting point.

Based on the findings of working with this case, we would recommend looking 
at best practices for further development. One good example could be charity 
navigator.
